Preliminary Thesis Defence

### 2013-12-28 PTD.tex
add results, rewrite data section

\maketitle
\tableofcontents
% \listoftables
% \listoffigures

@@

\begin{refsection}
\chapter{Bitcoin and Remitances: The Potential of `Stupid Phones'}
\label{btc}
In the 2009 whitepaper \parencite{nakamoto2008bitcoin} called \citetitle{nakamoto2008bitcoin} an anonymous individual or collective referred to a Satoshi Nakamoto (the Japanese equivalent of John Smith) describes an online currency called Bitcoin (BTC). 
This currency -the first of a group called cryptocurrencies- has the following economics features:

\begin{itemize}
\item public transactions
\item anonymous addresses
\item fixed amount of units
\item high granularity (1 Bitcoin = 100,000,000 Satoshi)
\item no or low transaction costs
\end{itemize}

An addition to these economic features, the key feature of Bitcoin is decentralisation.
All transactions are kept in a public ledger called the blockchain. An incentive in the form of transaction fees is provided to stimulate the creation of multiple copies of this ledger.
Conflict resolution, in this system, is done through majority consensus of blockchain copy holders.

There are a number of features which make Bitcoin attractive for remittances. Firstly, the low transaction costs are a huge step up from the current facilitators, which charge high percentages. Secondly, government intervention (especially in the recipient country) is prevented by the anonymity. Thirdly, recipients can choose to keep their remittance in a currency which is not controlled by their government. Fourthly, the granularity ensures very small transactions can be conducted.

Bitcoin initially because popular in advanced economies such as those in Europe and North America.
However, since mid 2013 there has been a large shift towards developing economies,
in which comparative advantages of Bitcoin are more pronounced.
For example, since its inception, Mt.Gox (located in Japan) was the largest Bitcoin exchange (marketplace), however in October 2013, Mt.Gox was overtaken by a Chinese exchange.

Bitcoin transactions are conducted by the electronic `signing' of a transaction.
This is a very simple electronic process.
Currently many smartphone apps are available to this purpose.
However, in the targeted developing economies, many phones are not smartphones, the vast majority using Nokia Operating System (Nokia OS).
 These phone can also run applications, using the Java Mobile App platform. Currently there are no Bitcoin apps available for this platform.

I propose to participate in the development of open-source applications which would enable the users of stupid phones.
We can then exploit the temporal difference when releasing the applications in different languages at different times,
as well the downloads from traceable IP addresses.

\section{Data}
\label{btc:data}
Funds held at Bitcoin exchanges are not held in the owners bitcoin wallet.
Rather, the exchange holds them in their wallet, and the clients have a claim on this wallet.
Much like the way bank clients have a claim to their money, which is in the bank's vault.

Therefore Bitcoin purchases at exchanges do not lead to transaction being recorded in the blockchain.
Since the Bitcoins remain in the Exchange's wallet, the only thing which changes is the claims of the clients.

\begin{itemize}
 \item The blockchain (public ledger)
 \begin{itemize}
 	\item IP address
 	\item Language of transaction notice
 	\item Transaction times
 \end{itemize}
 \item The exchanges
 \begin{itemize}
 	\item Location of exchanges
 	\item Transaction costs for each currency
	\item The order books
	\item Transaction times
 	\item The traded currency
 \end{itemize}
 \item Software
 \begin{itemize}
 	\item Downloads
 	\item Translation contributions (?)
 	\item Connections to server
 \end{itemize}
\end{itemize}

\printbibliography
\end{refsection}

\begin{refsection}
\chapter{Bitcoin Attacks: Or how cryptocurrencies gain momentum}
As discussed in \autoref{btc}, there has been a new phenonemon in international finance called cryptocurrencies. The first of these was the cryptocurrency called Bitcoin \parencite{nakamoto2008bitcoin}. However, soon after Bitcoin started gaining momentum, alternative crypotcurrencies where being designed. All of these cryptocurrencies are based to a large extend on the Bitcoin protocol, but often introduce small technological innovations.

The most known of all of these alternative crypocurrencies is Litecoin. Litecoin introduces a number of small technological innovations, the most import of these is the change that the process of `mining' coins is 4 times faster, this has two consequences, transactions are approved faster than in the bitcoin protocol. It also means that the technological limit for the total number of Litecoins ever available is 4x times higher. For Bitcoin the technical limit is around 21 million Bitcoin, which is expected to be reached in the year 2140. For Litecoin, the limit is around 84 million bitcoin, which is also expected to be reached around this time.

The key thing to note here is the perspective of the new cryptocurrecy adopt. Even though the value of Bitcoin is much higher than that of Litecoin, it does not have more to offer. The lower valued new cryptocurrency is technologically superior and thus more attractive. Most new cryptocurrencies do not gain momentum and their value is only trivialy more than zero. However, some currencies have gain momentum, the previously mentioned litecoin introduces a technological innovation and build it base on that. However, recently a new cryptocurrency has arisen and become quite popular. This cryptocurrency is called `Dogecoin' and besides it name, it does not introduce any novelty. Dogecoin is a reference to an internet phenomenon called `Doge Meme'. Despite the fact that `Dogecoin' does not have a real reason for being considered valuable (in the sense that crypotocurrencies are considered valuable), however, by utilising a previously existing internet phenomenon, and it's fanbase, this currencies has become valuable. We thus observe that from the perspective of economic and technological fundamentals, there is a situation of multiple equilibria.

My idea is to adapt standard models of currency attacks such as in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models} to model the gaining of long (v.s.~currency attacks' short) momentum for cryptocurrencies. Initially we would model how a currency can gain sufficient momentum to establish itself as a stably above zero.

This could later be expended to a model with several cryptocurrencies competing for the investment of the same new cryptocurrency adopt, who is converting his/her fiat currency into one of several cryptocurrencies.

\begin{figure}
\caption{A Doge Meme}
\label{doge}
%\includegraphics[scale=0.8]{doge.jpg}
\end{figure}

\printbibliography
\end{refsection}

\begin{refsection}
\chapter{End notes}
\label{end-notes}
In the previous chapters I have presented my current research projects.
These projects are in various stages of completions.

I believe that my South Africa paper provides an interesting opportunity to exploit the data from the household survey,
done before and after a highly relevant policy change.
Especially since the methodology and location are the same as in \textcite{duflo2000child, duflo2003grandmothers}.
In addition to this there is now a third data wave which has become available.
This provides us with more data, and mostly the opportunity to use more interesting methodology.
The text of the paper still has to be written.

% The replication of Surviving Andersonville is already completed in term of the replication in Stata.
% We would like to redo the analysis in R \parencite{R}.
% The relevance of this for replications can be seen from the recent replication \textcite{bell2013questioning} of the original \textcite{rauchhaus2009evaluating} paper.
% The findings of this replication can summarised as:

%\begin{quote}
%``We were easily able to replicate Rauchhaus’ key findings in Stata, but couldn't get it to work in R. It took us a long while to work out why, but the reason turned out to be an error in Stata: Stata was finding a solution when it shouldn’t'have (because of separation in the data). This solution, as we show in the paper, was wrong – and led Rauchhaus’ paper to overestimate the effect of nuclear weapons on conflict by a factor of several million.''~\parencite{bell2013questioning}
%\end{quote}

% We do not expect to find anything similar to Bell and Miller,
% but think that it can nevertheless be interesting to replicate findings using a different software package.
% In R, we can replicate this using the package called `survival', which supports the Kaplan Meier and NPMLE methods.
% In addition to this, the paper needs to be rewritten to emphasise the key finding of our replication.

The discussion of \textcite{morris1998unique} is in a very early stage.
I have looked at the paper in detail, I have also done a brief analysis of my main critique,
namely the conflation of risk (quantifiable) and Knightian uncertainy (unquantifiable).
However, I would like to presenta worked out example which demonstrates how this convolution leads to the main result of the paper.
In addition to this, this example should demonstrate how only a part of the `ripe for attack' region is solved for the unique equilibrium.

Finally, relating to Bitcoin \parencite{nakamoto2008bitcoin}, I think that there is a enormous potention for uncontrolled low-cost remintances using Bitcoin. I would like to analyse the spread of this. I propose to follow the spread of applications for platforms which are popular in developing economies.

At this point, three out of four of the previously discussed research projects are some form of a replication of prior work. As replications they are mostly critiques of others' work, rather than constructive ideas. This is mostly a result of the fact that these projects progress faster. For this reason, these research projects have progressed more than the projects which are primarily based on my own ideas. However, it is my attention to shift the focus of my thesis to include more original work. Here I present two more ideas which are too preliminary to include in the main body of the text, but are based on my own work.

Firstly, I was in charge of setting up a baseline diagnostic into security perceptions in Conakry, Guinea. This diagnostic will be used to analyse the impact of a police reform conducted here. The reform constitutes of the implementation of a model of `police de proximitee'. The baseline consist of 4500 interviews using smartphones in the comune of Conkary as well a large number of interviews in N'Zerekore (east Guinea). Some time after the implementation of the police reform as follow up study will be conducted. I propose to conduct an impact evaluation using the results from the studies in which I have taken and will take part.

Secondly, I have previously studied philosophy of science in my bachelors in Theoretical Philosophy. I would like to write one paper about an issue relating to this. In particular I would like to at the effect of outliers. The effect how these outliers has extensively been discussed in contexts such as finance and international economics \parencite{taleb2010black,   sornette2009dragon},  as well as indiviual behaviour \parencite{kahneman2011thinking}. I would like to see how these principles affect research in development microeconomics.

In this document I have tried to give a description of my research projects. None of these projects are near completion and many are in fact in a very early stage. The purpose of this has been to describe the direction I am taking with my thesis, and to receive feedback on this. As a result of this being work in progress, the articles are still incomplete, this includes lacking the proper attribution of ideas using citations.

\printbibliography
\end{refsection}

>>>>

\maketitle
\tableofcontents

@@

\input{bitremit.tex}

\input{bitattack.tex}

\input{endnotes.tex}

### 2013-12-28 south-africa.tex
add results, rewrite data section

This study deviates from the Duflo study in several ways.
First of all, the data from the \textcite{saldru2008nids,saldru2012nids} surveys, contains actual information on income,
including pension recipient status.
Whereas Duflo uses age as a proxy for recipient status.
Secondly, between mid 2008 and the end of 2009 the pension age for men was gradualy lowered to sixty, which is at par with women.
Another deviation is the usage of \textcite[WHO Child Growth Standards]{who2006child} in stead of \textcite[CDC Growth Charts: United States]{nchs2000cdc}.
Since these have superseded the CDC charts, however this should not be of any consequence.

The main preliminary result is that the household effect (i.e. having one or more recipients in the household),
is very insignificant in the 2008 estimate.
But in the 2012 estimate it is very significant.

\section{Data}
\label{sa:data}
In this paper I use data from two sources.
The first is the South African National Income Dynamics Survey \parencite[NIDS]{saldru2008nids, saldru2012nids, saldru2013nids} and the second is the World Health Organization's Child Growth Standards \parencite[WHO]{who2006child}.

The main source of data is the NIDS.
This survey collects data on a representative set of appproximately 10,000 South-African households.
The primary information types I use are, the child anthropometrics, the age and gender of household members, and the status as state pension recipients.

@@

Children's anthropometrics are taken, these are length/height, weight, and waist.
Using these anthropometics and WHO growth standards, z-scores have been calculated.
Unfortunately wave 2 (2012) accidentally omitted the z-scores, so that these cannot be evaluated until an updated version is published.
However, I have computed the length-for-age z-scores manually.

In 2006 the WHO published its standards for child growth \parencite{who2006child}.
These standards are based on the scores of children from different ethnic populations in households which observed a healthy lifestyle.
The standards provide the means and standards deviations used. 
These are on a monthly basis for height-for-age, and on a semi-centimeter level for weight-for-height scores.

\section{Identification Strategy
\label{sa:identification}}
The policy change, a natural experiment

the ATET, etc.

\subsection{The estimation using OLS}
Our first estimation method uses OLS.

\subsection{Difference in Differences}
The estimation using diff-in-diff, its equivalence to fixed-effects, and how it is different when using T=3.

\section{Obsolete: Analysis}
\label{sa:analysis}
I perform three types of analysis.
The first analysis uses the Duflo method, whereby I compute the z-scores (using WHO in stead of CDC, this is of no consequence)
and then compare based on living in the household with an of-pension-eligible adult.
Secondly, I use my computed z-scores and the data set provided variable which describes the actual pension received (or lack thereof).
Lastly, I use this state pension variable to evaluate the z-scores provided in the dataset.

The first type of analysis is almost identical to Duflo.
Using an internation set of standard anthropometrics for healthy children between 6 and 60 months old, I standarize observed anthropometrics.
I then construct a number of dummies of different ages and gender of the pension recipients.

In the second analysis, I use the same z-scores I calculated for the Duflo method.
However, here I use the state pension recipient variable provided by the NIDS data set.
For simplicity I change the numerical variable to a dummy variable (as the benefits are virtually identical this is without much loss of information).

This method uses the pre calculated z-scores from the data set and the state pension dummy.
Unfortunately the 2012 z-scores are missing except for height-for-age.
I therefore use only the height-for-age z-scores for the 2012 estimates.

In all of these methods the z-scores can be compared on a number of properties.
Firstly, the status of living in the same household as a state pension recipient or not is the first property to compare.
Secondly, when living with a recipient,the effects of male and female recipients can be compared.
Thirdly, the effects based on the gender of the child can be compared.

>>>>

This study deviates from the Duflo study in several ways.
% MAIN DEVIATION, PANEL NATURAL EXPERIMENT
First of all, the data from the \textcite{saldru2008nids,saldru2012nids} surveys, contains actual information on income,
including pension recipient status.
Whereas Duflo uses age as a proxy for recipient status.
Secondly, between mid 2008 and the end of 2009 the pension age for men was gradualy lowered to sixty, which is at par with women.
Another deviation is the usage of \textcite[WHO Child Growth Standards]{who2006child} in stead of \textcite[CDC Growth Charts: United States]{nchs2000cdc}.
Since these have superseded the CDC charts, however this should not be of any consequence.

% THE IMPERTUS FOR THE PAPER IS THE GENDER IN CCTs and OPTIMAL DESIGN
% RELATES TO THE ISSUE OF HOUSEHOLD AS A UNIT
% THEY ARE NO LONGER THAT RARE IN DEVELOPING COUNTRIES ???

% HISTORY OF APARTHEID AND CHANGE IN PENSION SCHEME

% STATE THE MAIN RESULT

\section{Data}
\label{sa:data}
% DESCRIPTIVE STATISTICS OF THE DATASET AND POSSIBLY THE GROWTH STANDARDS
In this paper I use data from two sources.
The first is the South African National Income Dynamics Survey \parencite[NIDS][]{saldru2008nids, saldru2012nids, saldru2013nids} and the second is the World Health Organization's Child Growth Standards \parencite[WHO]{who2006child}.

\subsection{South Africa: National Income Dynamics Survey}
The main source of data is the National Income Dynamics Survey of South Africa \parencite{saldru2008nids, saldru2012nids, saldru2013nids}.
This survey collects data on a representative set of appproximately 10,000 South-African households over time.
The primary information types I use are:
\begin{itemize}
  \item child anthropometrics,
  \item child age (in days)
  \item adult pension recipient status
  \item adult pension recipient gender
\end{itemize}

@@

Children's anthropometrics are taken, these are length/height, weight, and waist.
Using these anthropometics and WHO growth standards, z-scores have been calculated.

\subsection{WHO: Child Growth Standards}
In 2006 the WHO published its standards for child growth \parencite{who2006child}.
These standards measure the difference between a child's anthropometrics
standardised against an ideal score.

Z-score anthropometrics are used since they are considered to be a good representation of a child's health,
and by extension, the household in which they grow up.
These ideal scores are based on a sample of children from different ethnic populations,
in households which observed a healthy lifestyle.
Any health issues, such as malnutrition or disease will affect these metrics,
by causing the child to be shorter or lighter.
However, it is impossible to distinquish between the causes of an observed slow growth.

We stay with the best practice of using only metrics for children between the ages of 6 months and 60 months.

In general, can distinquish between two types of anthropometric z-scores, the age-based z-scores and the height-based z-scores.
Whereby `based' refers to the reference point at which anthropometrics are standardised.

\subsubsection{Age-Based Z-scores}
The age-based z-scores are the Height-for-Age Z-score (HAZ) and the Weight-for-Age Z-score (WAZ).
Since these metrics are age-based, they provide information about all past growth issues,
any past issues such a malnutrition and disease will have impaired growth,
and these effects will still be captured by today's height.

The age-based z-scores are constructed on a weekly basis up to the age of 60 months, and on a monthly basis thereafer.

\subsubsection{Height-Based Z-scores}
The height-based z-scores are the Weight-for-Height Z-score (WHZ)
and Body Mass Index Z-score (BMIZ).
Where the BMI (or Quetelet) is a transformed version of the WHZ, which has a quadratic height effect.
The equation for BMI is:
\[
\textbf{BMI} = \frac{\textbf{weight(kg)}}{\textbf{height(m)}^2}
\]

These scores compare children with others of the same height, irrispective of their age.
As a results we only observe the relatively short-term effect of weight.
The height-based metrics thus provide is with a short-term insight.

The height-based z-scores are available on a semi-centimeter level throughout all heights.

\subsection{Data Structure}
The NIDS uses a file and data structure which is ill suied for panel data analysis.
We therefore transform the data to a format which is more conducive to our analysis.
In doing so, we try to stay as close as possible to the`Tidy data' structure, as described in \textcite{wickham2014tidy}.
This is easiest using the R package `Reshape2' by the same author \parencite[Reshape2 implementation]{wickham2007reshaping}.

\section{Research Design}
\label{sa:identification}
% The policy change, a natural experiment

\subsection{Ordinary Least Squares}
We first perform an Ordinary Least Squares estimation (OLS).
This is done using the linear model (lm) procedure from the R package `Base' \parencite{R}.

\subsection{Difference in Differences}
In order to fully exploit the available data and the policy change,
we also employ a `Difference-in-Differences' estimator (DiD).
This estimator operationalised by using the fixed-effects (within) estimator, with a time-effect\footnote{The time effect estimated here is symmetric to the individual effect.
We use the term `time effect', since this is a more meaningful description of the policy change.}.

We perform the estimations using the R package `PLM' \parencite[see][]{croissant2008panel}.
It is worth noting  that questions have been raised about the Difference-in-Difference estimator being employed in certain situations,
for example by (ironically) \textcite{bertrand2004much}.

\subsubsection{Formal DiD Specification}
% ATET etc.

\section{Results}
In \autoref{sa:hazwaz} we present our estimation results for the age-based z-scores,
and in \autoref{sa:whzbmiz} we present our estimation results for the height-based z-scores.

% LaTeX table created manually
% Fri Dec 27 23:22:00 2013
\begin{table}[h!]
\centering
\caption{Estimation Results: HAZ \& WAZ}
\label{sa:hazwaz}
\begin{tabular}{l|rrr|rrr}
% \hline
& \multicolumn{3}{c}{Height for Age Z-score} & \multicolumn{3}{c}{Weight for Age Z-score}\\
\hline
specification & 1 & 2 & 3 & 1 & 2 & 3\\
\hline
w\_spen\_m & 0.2366 & *0.8228 & 0.7908 & 0.2366 & 0.2981 & 0.4780 \\
w\_spen\_w & -0.2331 & 0.1053 & 0.1072 & -0.2331 & -0.3112 & -0.3280 \\
elig.men.60 & & **-0.3419 & **-0.3465 & & ***-0.3475 & **-0.3243 \\
w\_spen\_m1:elig.men.60 & & & 0.0446 & & & -0.2545 \\
% \hline
w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 & -0.0000 & -0.0000 & -0.0000 \\
\end{tabular}
\end{table}

% LaTeX table created manually
% Fri Dec 27 23:53 2013
\begin{table}[h!]
\centering
\caption{Estimation Results: WHZ \& BMIZ}
\label{sa:whzbmiz}
\begin{tabular}{l|rrr|rrr}
& \multicolumn{3}{c}{Weight for Height Z-score} & \multicolumn{3}{c}{Body Mass Index Z-score}\\
\hline
specification & 1 & 2 & 3 & 1 & 2 & 3 \\
\hline
w\_spen\_m &  -0.3532 & -0.3210 & -0.4303 & *-0.8058 & *-0.7905 & *-1.0226 \\
w\_spen\_w & 0.0655 & 0.0371 & 0.0478 & -0.1592 & -0.1956 & -0.1742 \\
elig.men.60 & & -0.1417 & -0.1574 & & -0.1674 & -0.2049 \\
w\_spen\_m1:elig.men.60 & & & 0.1484 & & & 0.3407 \\
w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 & -0.0000 & 0.0000 & 0.0000
\end{tabular}
\end{table}

\subsection{Robustness Checks}

\subsubsection{OLS Robustness}

\subsubsection{DiD Robustness}
% HAUSMAN TEST FOR FE / RE

\section{Conclusion}

### 2013-12-28 uncertainty.tex
add bitcoin attacks
add results, rewrite data section

\begin{refsection}
\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}

@@

\section{The Idea}
\label{unc:idea}
\textcite{morris1998unique} addresses the issue of multiple equilibria in models of currency attacks.
In situations of a currency peg, there is the possibility of a currency attack.
Speculators are able to short the pegged currency, hoping the government will release the peg.
If a sufficiently large proportion of the market participates in this,
the cost of maintaining the peg for the government becomes too high,
which will lead to the government releasing the peg.
Currency attacks thus have a self-fulling nature,
which leads to a situation of multiple equilibria,
as described in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}.

@@

\subsection{The possible outcomes}
When we set \autoref{unc:specPO} and \autoref{unc:govPO} equal to zero,
we derive the two turning points in the model.
We define $\underaccent{\bar}{\theta}$ which solves $c(0, \theta) = \nu$.
Also, $\bar{\theta}$ solves $f(\theta) = e^* - t$.

>>>>

\begin{refsection}
\chapter{Risk and Uncertainty in Unique Equilibria in Currency Attacks}
\label{unc}

@@

\section{The Paper}
\label{unc:idea}
\textcite{morris1998unique} addresses the issue of multiple equilibria in models of currency attacks.
In situations of a currency peg, there is the possibility of a currency attack.
Speculators are able to short the pegged currency, hoping the government will release the peg.
If a sufficiently large proportion of the market participates in this,
the cost of maintaining the peg for the government becomes too high,
which will lead to the government releasing the peg.
Currency attacks thus have a self-fulling nature,
which leads to a situation of multiple equilibria,
as described in \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}.

@@

\subsection{The Possible Outcomes}
When we set \autoref{unc:specPO} and \autoref{unc:govPO} equal to zero,
we derive the two turning points in the model.
We define $\underaccent{\bar}{\theta}$ which solves $c(0, \theta) = \nu$.
Also, $\bar{\theta}$ solves $f(\theta) = e^* - t$.
